Variational Monte Carlo on bosonic systems

### 2018-03-09 project_1/article/article.tex
More results on problem b.

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
% Import physics package to include bra-ket
\usepackage{physics}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include package for drawing Feynman diagrams
\usepackage{tikz-feynman}
% Include package for typesetting contractions
\usepackage{simpler-wick}
% Include the Feynman-slash
\usepackage{slashed}
% Include Tikz
\usepackage{tikz}

@@

        INSERT PSEUDO-CODE DESCRIPTION OF

@@

	\subsection{Non-Interacting Systems}
	Initially we are interested in seeing how our implementation performs and to what extent it functions properly.
	the logical thing to do would be to look at a non-interacting system with a simple Gaussian wavefunction and
	harmonic oscillator potential. Such a system has a simple closed-form analytic solution\footnote{A fact that every 
	undergraduate physics student should be well aware of.}, which is further simplified by the "god-given" analytic
	units (\autoref{eq:closed_form_natural_units_local_energy}). By insertion of the analytically optimal

	We will start without importance sampling, that is by employing the simpler and more naïve "brute force" Monte Carlo
	sampling. Moreover, we will

>>>>

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
% Import physics package to include bra-ket
\usepackage{physics}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include package for drawing Feynman diagrams
\usepackage{tikz-feynman}
% Include package for typesetting contractions
\usepackage{simpler-wick}
% Include the Feynman-slash
\usepackage{slashed}
% Include Tikz
\usepackage{tikz}
% Several figures in the same figure
\usepackage{subfig}

@@

        INSERT PSEUDO-CODE DESCRIPTION OF ALGORITHM?

@@

	\subsection{Non-Interacting Systems}
	Initially we are interested in seeing how our implementation performs and to what extent it functions properly.
	the logical thing to do would be to look at a non-interacting system with a simple Gaussian wavefunction and
	harmonic oscillator potential. Such a system has a simple closed-form analytic solution\footnote{A fact that every 
	undergraduate physics student should be well aware of.}, which is further simplified by the "god-given" analytic
	units (\autoref{eq:closed_form_natural_units_local_energy}). This expression is minimised for 
	$\alpha = \frac{1}{2}\omega$. We also set $\omega = 1$ and get an expression for the 
	expected minimum local energy,
	\begin{equation}
		E_L(\vb{r}) = \frac{dN}{2},
	\end{equation}
	which will be used as the benchmark we are ultimately aiming for.

	We will start without importance sampling, that is by employing the simpler and more naïve "brute force" Monte Carlo
	sampling. Moreover, we will compute the value for the local energy analytically as well as with a numerical approach. 
	In the numerical approach.

	\begin{table}
		\caption{Analytic result. $N=1$, 1D, $2\times10^6$ cycles.}
		\centering
		\begin{tabular}{ccc} \hline
			\alpha & E($\alpha$) & $\sigma^2$(E) \\ \hline \hline
				0.30 & 0.5717 & 0.1504 \\
				0.34 & 0.5397 & 0.0815 \\
				0.38 & 0.5197 & 0.0390 \\
				0.42 & 0.5084 & 0.0154 \\
				0.46 & 0.5016 & 0.0034 \\
				0.50 & 0.5000 & 0.0000 \\
				0.54 & 0.5016 & 0.0030 \\
				0.58 & 0.5047 & 0.0117 \\
				0.62 & 0.5114 & 0.0239 \\
				0.66 & 0.5203 & 0.0381 \\
				0.70 & 0.5275 & 0.0590 \\ \hline \hline			
		\end{tabular}	
	\end{table}

	\begin{table}
		\caption{Numerical result. $N=1$, 1D, $2\times10^6$ cycles.}
		\centering
		\begin{tabular}{ccc} \hline
			\alpha & E($\alpha$) & $\sigma^2$(E) \\ \hline \hline
				0.30 & 0.5807 & 0.2535 \\
				0.34 & 0.5379 & 0.1280 \\
				0.38 & 0.5365 & 0.1120 \\
				0.42 & 0.5220 & 0.0671 \\
				0.46 & 0.5210 & 0.05250 \\
				0.50 & 0.5265 & 0.0411\\
				0.54 & 0.5264 & 0.0263 \\
				0.58 & 0.5353 & 0.0259 \\
				0.62 & 0.5481 & 0.0221 \\
				0.66 & 0.5481 & 0.0194 \\
				0.70 & 0.5596 & 0.0204 \\ \hline \hline
		\end{tabular}
	\end{table}

	\begin{table*}[ht]
		\centering
		\caption{Brute force Metropolis-Hasting at optimum value $\alpha = \frac{1}{2}$ in three dimensions. Step length = 0.1.}
		\begin{tabular}{c|ccc|ccc} 
			  & \multicolumn{3}{c|}{Analytic} & \multicolumn{3}{c}{Numeric} \\ \hline
			No. of particles & E($\alpha$) & $\sigma^2$(E) & CPU time [s] & E($\alpha$) & $\sigma^2$(E) & CPU time [s] \\ \hline
			1					 	&   1.5000		  & 0.0000			&  0.42562		& 1.29538		 & 0.10489		   & 0.69979  \\
			10						& 15.0000		  & 0.0000			&  0.78426 		& 7.70527		 & 3.91873		   & 7.06599	 \\
			100					&  150.0000	  & 0.0000			&  4.34369		& 74.22956 	 & 29.77369		   & 481.69100\\
			500					&	..				  & 0.0000			&  .. 					& ..	    			 & ..					   & \\ \hline
		\end{tabular}
	\end{table*}
